\bf On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2024-04-10 manuscript/manuscript.tex
first pass at UG section - will smooth later

% Graduate level
The misuses of one-sample KS test can be easily incorporated into graduate level
classroom teaching for courses that cover parametric bootstrap. For example, at
the University of Connecticut (UConn), JY has always included a demonstration of
the misuse under unspecified parameters in STAT 5361, Statistical Computing. The
catalog description of this course includes is: ``Use of computing for statistical
problems; obtaining features of distributions, fitting models and implementing
inference. Basic numerical methods, nonlinear statistical methods, numerical
integration, modern simulation methods.'' Bootstrap is covered under ``modern
simulation methods.''  The course is open to graduate students in Statistics,
others with permission. Detailed R code and graphical illustrations available in
the open-access course notes elucidate the distinctions between employing null
hypotheses with and without defined parameters (accessible at:
\url{https://jun-yan.github.io/stat-5361/boot.html#parametric-bootstrap}).
Students were able to follow the demonstration closely, gaining a clear
understanding of the implications of using estimated parameters within test
statistics, and learning about the efficacy of the parametric bootstrap method
as a corrective measure.

@@

% Undergraduate level (could mention AZ's undergraduate thesis)

>>>>

% Graduate level
The misuses of one-sample KS test can be easily incorporated into graduate level
classroom teaching for courses that cover parametric bootstrap. For example, at
the University of Connecticut (UConn), JY has always included a demonstration of
the misuse under unspecified parameters in STAT 5361, Statistical Computing. The
catalog description of this course includes: ``Use of computing for statistical
problems; obtaining features of distributions, fitting models and implementing
inference. Basic numerical methods, nonlinear statistical methods, numerical
integration, modern simulation methods.'' Bootstrap is covered under ``modern
simulation methods.''  The course is open to graduate students in Statistics,
others with permission. Detailed R code and graphical illustrations available in
the open-access course notes elucidate the distinctions between employing null
hypotheses with and without defined parameters (accessible at:
\url{https://jun-yan.github.io/stat-5361/boot.html#parametric-bootstrap}).
Students were able to follow the demonstration closely, gaining a clear
understanding of the implications of using estimated parameters within test
statistics, and learning about the efficacy of the parametric bootstrap method
as a corrective measure.

@@

% Undergraduate level (could mention AZ's undergraduate thesis)
At the undergraduate level, so far only the misuses of one-sample KS test have 
been presented and demonstrated in a classroom setting. At UConn, ES 
incorporated this material in STAT 3215, Applied Linear Regression in Data 
Science, in the context of residual diagnostics and testing whether the 
externally studentized residuals can be viewed as realizations of a standard 
normal distribution for large samples. The catalog description of this course 
states the following topics: ``Applied multiple 
linear regression analysis in data science, with an emphasis on modern 
statistical regression methods: simple linear regression and correlation 
analysis, multiple linear regression, analysis of variance, goodness of fit, 
comparing regression models through partial and sequential F tests, dummy 
variables, regression assumptions and diagnostics, model selection and penalized 
regression, prediction and model validation, principles of design of experiments, 
one-way and two-way analysis of variance.'' Students in this course are required
to have taken either two semesters of introductory statistics or a 
Calculus~2-based statistical methods course as a prerequisite.  While students 
in the class are exposed to the bootstrap in the context of linear regression 
models, they are not in general familiar with serially dependency.  Thus, the 
remedies and more complicated serially dependent settings were not presented at 
the undergraduate level.  Serial dependence is covered in other
undergraduate courses, and in fact, the contents of this manuscript were the 
basis of AZ's undergraduate honors thesis. All concepts are certainly within 
reach of UConn undergraduate Statistics and Statistical Data Science majors.
